### 2023-02-07 article.tex
Improvements

@@

\subsubsection{Code must be clean}

Code gives an indication of the quality 
of a computational experiment and several metrics are
devised to get an idea of the quality of code.

\paragraph{SLOC}

The simplest metric to assess the quality of code is 
the amount of (single) lines of code (SLOC). 
Code that has a lower SLOC count, i.e. it is more concise,
is usually regarded as having a lower chance of containing bugs.
Additionally, following a style guide 
(e.g. the Tidyverse style guide \cite{wickham2019advanced} for R,
or PEP 8 \cite{van2001pep} for Python), 
improves software quality \cite{fang2001}.

\paragraph{Cyclomatic complexity}

A more interesting metric is the cyclomatic complexity of the code.
The cyclomatic complexity is approximately defined 
as the number of independent paths that
the code can be executed. 
For example, code that has only one \verb|if| statement
has a cyclomatic complexity of 2, as the condition within the \verb|if|
statement can be true or false,
resulting in the body of the \verb|if| statement being either
exectuted or ignored.
The cyclomatic complexity correlates with code complexity,
where more complex code is likelier to contain or give rise to bugs 
\cite{abd2018calculating,chen2019empirical,zimmermann2008predicting}

>>>>

Code as paradata has multiple uses:
(1) to reproduce an experiment, by running the unchanged code on the same data as
used in a published research,
(2) to replicate an experiment, by running the unchanged code on different data as
used in a published research,
(3) to extend an experiment, by changing the code.

@@

\paragraph{Coding style}

Code is just 'another kind of data' and should be designed 
as such, for example, by using tools to work on it \cite{wilson2022twelve}.
A first example is to use a tool to enforce a coding style 
(e.g. the Tidyverse style guide \cite{wickham2019advanced} for R,
or PEP 8 \cite{van2001pep} for Python).
Following a consistent coding style improves software quality \cite{fang2001}.
A second example is to use a tool to enforce a low cyclomatic complexity.
The cyclomatic complexity is approximately defined 
as the number of independent paths that
the code can be executed. 
For example, code that has only one \verb|if| statement
has a cyclomatic complexity of 2, as the condition within the \verb|if|
statement can be true or false,
resulting in the body of the \verb|if| statement being either
exectuted or ignored.
The cyclomatic complexity correlates with code complexity,
where more complex code is likelier to contain or give rise to bugs 
\cite{abd2018calculating,chen2019empirical,zimmermann2008predicting}
